Towards a Cognitive System That Can Recognize Spatial Regions Based on Context

### 2012-01-24 scenarios/cdsr/trunk/papers/AAAI2012/evaluation.tex
added results...

To evaluate our progress toward building a cognitive system capable of reasoning about these CDSRs, we conducted the an experiment focusing on the following questions:
\begin{itemize}
\item{How well do anchor points capture context-dependent spatial regions?}
\item{When provided with a base representation containing a labelled CDSR, how well does our approach identify the CDSR in a given target?}
\item{Is the integration of geometric and semantic knowledge necessary?}
\item{Does similarity correlate with performance?}
\end{itemize}

I'm not sure how many of the above questions we want to talk about. The last one is fairly easy and won't take up much space in the paper. The integration of knowledge question is could take some more work as the grouping is determined by semantic type, so in testing just positional knowledge,  I would have to create an alternate set of anchor points.

@@

To determine how non-experts define CDRSs, we asked \textbf{SOMENUMBER} of users to draw polygons for each region type for each room. This task was performed using a webpage (link removed for blind review) shown in the inset in Figure~\ref{fig:ug40} on which each user was presented with an image of the real room plus the map data generated by the robot (as in Figure~\ref{fig:rooms}) onto which the drawing could be done. Users were also shown a polygon drawn by another user and asked to determine if it was an acceptable depiction of the region. All users provided acceptable regions, and therefore, we define the \textit{target region} as the union of the user-defined polygons. The user-provided data provides the ground truth against which we evaluate our transfers.

@@

As a baseline, we compare the transfer results against our manually encoded CDSRs for the target and a region that represents the entire room. Results on the entire room provide a baseline performance measure. The performance of the manually encoded CDSRs evaluates how well the anchor points capture the user defined regions and a ceiling for the inferred region performance.

\subsection{Results}
\begin{table}
\small
\caption{Performance by Room}
\begin{tabular}{|c|c|c|c|}
\hline
Room & Transfer & Manually Encoded & Entire Room \\
\hline
Classroom-1 & p=nil,r=nil & p=.93,r=.60 & p=.23,r=1 \\
Classroom-2 & p=nil,r=nil & p=.90, r=.69 & p=.19,r=1 \\
Classroom-3 & p=nil,r=nil & p=.94,r=.64 & p=.17,r=1 \\
Classroom-4 & p=nil,r=nil & p=85,r=.89 & p=.19,r=1 \\  %This is 222-Classroom
Classroom-5 & p=nil,r=nil & p=.87,r=.71 & p=.24,r=1 \\ % This is 222-Seminar
Classroom-6 & p=nil,r=nil & p=.76,r=.66 & p=.20,r=.99 \\ % This is UG40
\hline
\end{tabular}
\end{table}

If we are just going to report means, we should standard deviations as well. %yup!

\begin{table}
\small
\caption{Performance by Region Type}
\begin{tabular}{|c|c|c|c|}
\hline
Region & Transfer & Manually Encoded & Entire Room \\
\hline
Front & p=nil,r=nil & p=.89,r=.79 & p=.23,r=1 \\
Back & p=nil,r=nil & p=.85,r=.82 & p=.13,r=1 \\
Front Rows & p=nil,r=nil & p=.85,r=.48 & p=.22,r=1 \\
Back Rows & p=nil,r=nil & p=.94,r=.40 & p=.7,r=.9 \\
Kitchen & p=nil,r=nil & p=nil,r=nil & p=nil,r=nil \\
Office & p=nil,r=nil & p=nil,r=nil & p=nil,r=nil \\
\hline
\end{tabular}
\end{table}

Or we could report all of the results in a single entry.

\begin{table}
\small
\caption{Performance against Target Region}
\begin{tabular}{|c|c|c|}
\hline
Transfer & Manually Encoded & Entire Room \\
\hline
p=nil,r=nil & p=.88,r=.66 & p=.20,r=.99 \\
\hline
\end{tabular}
\end{table}

% this would be lovely!

Overall the transferred region was significantly better than the entire room (p<Blah), and not statistically different than the manually encoded region (p=Blah). There was a positive correlation (r=Blah) between the structural evaluation score of the analogy and f-measure of the inference.

@@

Our results

>>>>

To evaluate our progress toward building a cognitive system capable of reasoning about these CDSRs, we conducted the an experiment focusing on the following questions:
\begin{itemize}
\item{Can anchor points capture context-dependent spatial regions?}
\item{When provided with a base representation containing a labelled CDSR, how well does our approach identify the CDSR in a given target?}
\end{itemize}

@@

To determine how people define CDRSs, we asked three users to draw polygons for each region type for each room. This task was performed using a webpage (link removed for blind review) shown in the inset in Figure~\ref{fig:ug40} on which each user was presented with an image of the real room plus the map data generated by the robot (as in Figure~\ref{fig:rooms}) onto which the drawing could be done. We call the each user-defined polygon a \textit{target region} against which we evaluate our transfers.

@@

We compare the transfer results against our manually encoded CDSRs for the target region and against a region that represents the entire room. Results on the entire room provide a baseline performance measure. The performance of the manually encoded CDSRs evaluates how well the anchor points capture the user defined regions and provides a ceiling for the inferred region's performance.

\subsection{Results}
\begin{table}
\small
\caption{Overall Performance}
  \label{tab:overall}	
\begin{tabular}{|c|c|c|}
\hline
Inferred & Manually Encoded & Entire Room \\
\hline
$\bar{p}$=.45 $\sigma$=.37, $\bar{r}$=.45 $\sigma$=.38 & $\bar{p}$=.71 $\sigma$=.29, $\bar{r}$=.66 $\sigma$=.24  & $\bar{p}$=.17 $\sigma$=.11, $\bar{r}$=.98 $\sigma$=.05  \\
\hline
\end{tabular}
\end{table}

\from{klenk}{I guess we should rotate the above table. And it has been awhile since I wrote academic, so feel free to cut the boring text below}

Table~\ref{tab:overall} summarizes the results by combining each problem instance and user-defined target region. The mean precision and recall for the inferred regions is .45 with a standard deviation of .37 and .38 respectively. When comparing the manually encoded regions against each target instance, we calculate a mean precision of .71 ($\sigma$=.29) and recall of .66 ($\sigma$=.24). The region defined by the room results in a precision of .17 ($\sigma$=.11) and recall of .98 ($\sigma$=.05).

\begin{table}
\small
\caption{Performance by Region Type}
  \label{tab:region}	
\begin{tabular}{|c|c|c|c|}
\hline
Region & Inferred & Manually Encoded & Entire Room \\
\hline
Front & $\bar{p}$=.33 $\sigma$=.34, $\bar{r}$=.52 $\sigma$=.40 & $\bar{p}$=.60 $\sigma$=.29, $\bar{r}$=.82 $\sigma$=.19  & $\bar{p}$=.15 $\sigma$=.09, $\bar{r}$=1 $\sigma$=0  \\
\hline
Back & $\bar{p}$=.45 $\sigma$=.35, $\bar{r}$=.56 $\sigma$=.40 & $\bar{p}$=.66 $\sigma$=.25, $\bar{r}$=.84 $\sigma$=.17  & $\bar{p}$=.11 $\sigma$=.06, $\bar{r}$=.99 $\sigma$=.03  \\
\hline
Front Rows & $\bar{p}$=.62 $\sigma$=.36, $\bar{r}$=.22 $\sigma$=.21 & $\bar{p}$=.82 $\sigma$=.30, $\bar{r}$=.50 $\sigma$=.11  & $\bar{p}$=.22 $\sigma$=.08, $\bar{r}$=1 $\sigma$=0  \\
\hline
Back Rows & $\bar{p}$=.74 $\sigma$=.28, $\bar{r}$=.43 $\sigma$=.23 & $\bar{p}$=.80 $\sigma$=.29, $\bar{r}$=.43 $\sigma$=.26  & $\bar{p}$=.19 $\sigma$=.06, $\bar{r}$=1 $\sigma$=0  \\
\hline
Kitchen & $\bar{p}$=.23 $\sigma$=.03, $\bar{r}$=.09 $\sigma$=.02 & $\bar{p}$=.78 $\sigma$=.20, $\bar{r}$=.71 $\sigma$=.13  & $\bar{p}$=.16 $\sigma$=.02, $\bar{r}$=.92 $\sigma$=.13  \\
\hline
Office & $\bar{p}$=.05 $\sigma$=.01, $\bar{r}$=.06 $\sigma$=.06 & $\bar{p}$=.78 $\sigma$=.29, $\bar{r}$=.55 $\sigma$=.20  & $\bar{p}$=.08 $\sigma$=.03, $\bar{r}$=.93 $\sigma$=.06  \\
Living Room & $\bar{p}$=0 $\sigma$=0, $\bar{r}$=0 $\sigma$=0 & $\bar{p}$=.63 $\sigma$=.34, $\bar{r}$=.54 $\sigma$=.13  & $\bar{p}$=.35 $\sigma$=.22, $\bar{r}$=.96 $\sigma$=.06  \\
\hline
\end{tabular}
\end{table}

Table~\ref{tab:region} separates the results by the region type of the context-dependent spatial region. The mean precision for the transferred regions ranged from .74 for the back rows to 0 for the living room of the studio apartment. Comparing the manually encoded against the target regions resulted in a minimum mean precision of .60, which occurred for the front of the classroom. The room precision, which is directly proportionally to the size of the target region, varied from .08 for the office to .35 for the living area.

%(3 :transfer-p (0.5649091160864536d0 . 0.3824746399624735d0)  :transfer-r (0.4264200799557943d0 . 0.34846457388485863d0) :self-p   (0.8290901572528112d0 . 0.19630847005535487d0) :self-r
%  (0.6113880445364026d0 . 0.22432810023132582d0) :room-p
%  (0.20903207305733315d0 . 0.10291204447091876d0) :room-r
%  (0.9960679285191474d0 . 0.011022662977174953d0))
% (2 :transfer-p (0.4496053675639215d0 . 0.36845133415546233d0)
%  :transfer-r (0.4174204919721308d0 . 0.3697742376406773d0) :self-p
%  (0.7556540963495391d0 . 0.2672139547143468d0) :self-r
%  (0.6252647119318083d0 . 0.23778540411202373d0) :room-p
%  (0.17891943994602752d0 . 0.11273973943366206d0) :room-r
%  (0.95742701954372d0 . 0.08432884603590181d0))
% (1 :transfer-p (0.3360804531954755d0 . 0.3364697224078454d0)
%  :transfer-r (0.5074731366878895d0 . 0.4231938085019586d0) :self-p
%  (0.5493333659045643d0 . 0.33190756014975015d0) :self-r
%  (0.7596761147032691d0 . 0.25387231566349d0) :room-p
%  (0.12277614149421091d0 . 0.10953121808467986d0) :room-r
%  (0.9946881982552835d0 . 0.011992196508589958d0))

@@

These results support the hypothesis that anchor points can provide a symbolic representation on top of sensor data for context-dependent spatial regions, and, when combined with qualitative spatial relations, they facilitated learning from a single example through analogical transfer. The relatively high manually encoded precisions and recalls indicate that the defined anchor points are a reasonable starting place for a symbolic representation. The lower scores typically resulted from target regions which were farther away from objects. While the inferred regions did not score as well as the manually encoded regions, they were considerably more precise than the room regions. The only case were transfer was not possible was between the two studio's living room cases. The objects which define the living area in one studio (sofa, TV, and bookshelves) are significantly different than the objects in the other (desk, bed, and sofa), as are the studios in general.
